Mapping plant-pollinator interactions across Europe

### 2024-01-25 Manuscript/Ms.qmd
minor organisation edits

@@

## Taxonomic coverage

@@

```{r echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, out.width="100%", fig.cap= "\\textbf{Figure 2}. Proportion of the major pollinator orders by habitat types and bioclimatic regions in the SafeNet database. The orders, from left to right, include Hymenoptera, Diptera, Lepidoptera and Coleoptera. The horizontal barplot on the right indicates the number of studies that were conducted on each habitat type or bioclimatic region. Note that a single study can countribute to more than one habitat or bioclimatic region. Areas with a greater number of studies are more likely to depict accurate proportions of pollinators in those systems.", fig.width=4, fig.height=4}
#Load data (done it in earlier chunks)
#Select cols of interest
data1 = data %>% 
select(Study_id, Network_id, Authors_habitat,
  Corine_land_cover, SafeNet_habitat, Bioregion,
  Latitude, Longitude, Day, Month, Year, Plant_rank,
  Plant_status, Plant_matchtype, Plant_accepted_name,Plant_order,
  Pollinator_rank, Pollinator_status, Pollinator_matchtype,
  Pollinator_accepted_name, Pollinator_order, Interaction)

@@

@@

>>>>

\newpage

@@

@@

## Habitat type and bioclimatic region

```{r echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, out.width="95%", fig.cap= "\\textbf{Figure 2}. Proportion of the major pollinator orders by habitat types and bioclimatic regions in the SafeNet database. The orders, from left to right, include Hymenoptera, Diptera, Lepidoptera and Coleoptera. The horizontal barplot on the right indicates the number of studies that were conducted on each habitat type or bioclimatic region. Note that a single study can countribute to more than one habitat or bioclimatic region. Areas with a greater number of studies are more likely to depict accurate proportions of pollinators in those systems.", fig.width=3.8, fig.height=3.8}
#Load data (done it in earlier chunks)
#Select cols of interest
data1 = data %>% 
select(Study_id, Network_id, Authors_habitat,
  Corine_land_cover, SafeNet_habitat, Bioregion,
  Latitude, Longitude, Day, Month, Year, Plant_rank,
  Plant_status, Plant_matchtype, Plant_accepted_name,Plant_order,
  Pollinator_rank, Pollinator_status, Pollinator_matchtype,
  Pollinator_accepted_name, Pollinator_order, Interaction)

@@

## Habitat type and bioclimatic region

@@

\newpage

# References
